Revisiting `Growth and Inequality in Public Good Provision' ---Reproducing and Generalizing Through Inconvenient Online Experimentation

### 2023-05-22 analysis/quarto/paper.qmd
add sample sizes to results sections

@@

Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups. @fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _Period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.

@@

@@

<!--
> "There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results. They are rarely the same, and the correct answer is (b)." [@bemwriting, p. 171]
-->

```{r generalizability_prep}
R1covs <- covs[, .(participant.code,
                   donation = donation * 20 ,
                   donationShare = (donation * 20) / payoff * 100,
                   age,
                   gender,
                   switching_row,
                   payoff)]
temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
temp[, contributionShare := ownContribution/20 * 100]
temp[, consistency := 1 - (contributionShare - donationShare)]
```

>>>>

```{r}
N_r <- R1[treatment == "replication", .N]
N_o <- R1[treatment == "noPunish10", .N]
```

Throughout this section, I pool data from both the citizens as well as the students from Hamburg and compare it with the students GMTV recruited in Nottingham. I refer to the two samples as the _reproduction sample_ ($N_r$ = `r N_r`) and the _original sample_ ($N_o$ = `r N_o`), respectively.

@@

Given the different samples and the possibility of endogenous growth--which essentially is the main feature of the game--I ask whether and how the inequality grows _within_ groups. @fig-gini-time-series illustrates that inequality did grow: at the end of the game, the original and the replication groups exhibit an average Gini coefficient of `r originalGini` and `r replicationGini`, respectively.^[The two-sided rank sum test (comparing differences between samples) yields a p-Value of `r rs1` for the mean Gini coefficient in last round of the game.] Because every participant started with the same initial endowment (in _period 0_, so to speak), every group started equally--with a Gini coefficient equaling zero.

@@

```{r}
N <- duration[, participant_code %>% unique() %>% length()]
```

Throughout this section, I do not consider GMTV's data and pool data I gathered from the citizens as well as the students from Hamburg (N = `r N`).

@@

```{r generalizability_prep}
R1covs <- covs[, .(participant.code,
                   donation = donation * 20 ,
                   donationShare = (donation * 20) / payoff * 100,
                   age,
                   gender,
                   switching_row,
                   payoff)]
temp <- R1[R1covs, on = .(participant.code = participant.code)][treatment == "replication"]
temp[, contributionShare := ownContribution/20 * 100]
temp[, consistency := 1 - (contributionShare - donationShare)]

N_s <- temp[student == TRUE, .N]
N_g <- temp[student == FALSE, .N]
```

As before, I do not consider GMTVs' data in this section. Instead, I will differentiate between data from the citizens and the students from Hamburg. I refer to the two samples as the _students_ ($N_s$ = `r N_s`) and the _general population sample_ ($N_g$ = `r N_g`), respectively.

### 2023-05-22 analysis/quarto/paper.tex
add sample sizes to results sections

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

@@

Given the different samples and the possibility of endogenous
growth--which essentially is the main feature of the game--I ask whether
and how the inequality grows \emph{within} groups.
Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
at the end of the game, the original and the replication groups exhibit
an average Gini coefficient of 0.23 and 0.22, respectively.\footnote{The
  two-sided rank sum test (comparing differences between samples) yields
  a p-Value of 0.6059 for the mean Gini coefficient in last round of the
  game.} Because every participant started with the same initial
endowment (in \emph{Period 0}, so to speak), every group started
equally--with a Gini coefficient equaling zero.

@@

@@

>>>>

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, frame hidden, enhanced, interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Throughout this section, I pool data from both the citizens as well as
the students from Hamburg and compare it with the students GMTV
recruited in Nottingham. I refer to the two samples as the
\emph{reproduction sample} (\(N_r\) = 116) and the \emph{original
sample} (\(N_o\) = 92), respectively.

@@

Given the different samples and the possibility of endogenous
growth--which essentially is the main feature of the game--I ask whether
and how the inequality grows \emph{within} groups.
Figure~\ref{fig-gini-time-series} illustrates that inequality did grow:
at the end of the game, the original and the replication groups exhibit
an average Gini coefficient of 0.23 and 0.22, respectively.\footnote{The
  two-sided rank sum test (comparing differences between samples) yields
  a p-Value of 0.6059 for the mean Gini coefficient in last round of the
  game.} Because every participant started with the same initial
endowment (in \emph{period 0}, so to speak), every group started
equally--with a Gini coefficient equaling zero.

@@

Throughout this section, I do not consider GMTV's data and pool data I
gathered from the citizens as well as the students from Hamburg (N =
151).

@@

As before, I do not consider GMTVs' data in this section. Instead, I
will differentiate between data from the citizens and the students from
Hamburg. I refer to the two samples as the \emph{students} (\(N_s\) =
64) and the \emph{general population sample} (\(N_g\) = 52),
respectively.
